---
output:
  md_document:
    variant: markdown_github
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```
curlconverter - Generate `httr` functions or parameters for use with `httr` from `cURL` commands.

Based on the [`curlconverter`](https://github.com/NickCarneiro/curlconverter) Node module by Nick Carneiro

The following functions are implemented:

- `straighten`: generate the data/function

### News

- Version 0.2.0 : Added parsed URL to return value of `straighten()`
- Version 0.1.0 released

### Installation

```{r eval=FALSE}
devtools::install_github("hrbrmstr/curlconverter")
```

```{r echo=FALSE, message=FALSE, warning=FALSE, error=FALSE}
options(width=120)
```

### Usage

```{r}
library(curlconverter)
library(jsonlite)

# current verison
packageVersion("curlconverter")

toJSON(straighten("curl 'http://financials.morningstar.com/ajax/ReportProcess4HtmlAjax.html?&t=XNAS:MSFT&region=usa&culture=en-US&cur=&reportType=is&period=12&dataType=A&order=asc&columnYear=5&curYearPart=1st5year&rounding=3&view=raw&r=973302&callback=jsonp1454021128757&_=1454021129337' -H 'Cookie: JSESSIONID=5E43C98903E865D72AA3C2DCEF317848; sfhabit=asc%7Craw%7C3%7C12%7CA%7C5%7Cv0.14; ScrollY=0' -H 'DNT: 1' -H 'Accept-Encoding: gzip, deflate, sdch' -H 'Accept-Language: en-US,en;q=0.8' -H 'User-Agent: Mozilla/5.0 (Macintosh; Intel Mac OS X 10_11_3) AppleWebKit/537.36 (KHTML, like Gecko) Chrome/47.0.2526.111 Safari/537.36' -H 'Accept: text/javascript, application/javascript, */*' -H 'Referer: http://financials.morningstar.com/income-statement/is.html?t=MSFT&region=usa&culture=en-US' -H 'X-Requested-With: XMLHttpRequest' -H 'Connection: keep-alive' -H 'Cache-Control: max-age=0' --compressed"), pretty=TRUE)

(curl_line <- readLines(system.file("extdata/curl5.txt", package="curlconverter"), warn=FALSE))

toJSON(straighten(curl_line), pretty=TRUE)

```

### Test Results

```{r}
library(curlconverter)
library(testthat)

date()

test_dir("tests/")
```

### Code of Conduct

Please note that this project is released with a [Contributor Code of Conduct](CONDUCT.md). 
By participating in this project you agree to abide by its terms.
