---
output: rmarkdown::github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

[![Build Status](https://travis-ci.org/hrbrmstr/curlconverter.svg?branch=master)](https://travis-ci.org/hrbrmstr/curlconverter) [![CRAN_Status_Badge](http://www.r-pkg.org/badges/version/curlconverter)](http://cran.r-project.org/package=curlconverter)
[![](http://cranlogs.r-pkg.org/badges/curlconverter)](http://cran.rstudio.com/web/packages/curlconverter/index.html)

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#",
  fig.path = "README-"
)
```
`curlconverter` - Generate `httr` functions or parameters for use with `httr` from `cURL` commands.

Based on the [`curlconverter`](https://github.com/NickCarneiro/curlconverter) Node module by Nick Carneiro

### Why `curlconverter`?

Deciphering web/`REST` API and XHR calls can be tricky, which is one reason why
internet browsers provide _"Copy as cURL"_ functionality within their "Developer Tools" pane(s). These `cURL` command-lines can be difficult to wrangle into an `httr::GET` or `httr:POST` request, but you can now "straighten" these "cURLs"" either from data copied to the system clipboard or by passing in a vector of cURL command-lines and getting back a list of parameter elements which can be used to form `httr` requests. These lists can be passed to another function to automagically make `httr` functions.

The following functions are implemented:

- `straighten`: convert one or more _"Copy as cURL"_ command lines into useful data
- `parse_query`: parse URL query parameters into a named list
- `make_req`: turn parsed cURL command lines into a `httr` request functions (i.e. returns working R functions)

### News
- Version 0.8.0 : See `NEWS` file.
- Version 0.7.0 : See `NEWS` file.
- Version 0.6.7 : Fixed bug in js module that caused the header parsing to fail if there was only one header. Fixes #4 (added this to the test suite)
- Version 0.6.6 : Code cleanup & documentation update
- Version 0.6.5 : Reads & sets cookies
- Version 0.6.1 : Improved README <https://github.com/hrbrmstr/curlconverter/issues/3>
- Version 0.6.0 : changed the idiom (examples below)
- Version 0.5.0 : `make_req` now actually _returns a working/callable R function_
- Version 0.4.0 : `make_req` turns the cURLs into `httr` requests
- Version 0.3.1 : handles `--header` now (fixes #1)
- Version 0.3.0 : Added `parse_query`
- Version 0.2.0 : Added parsed URL to return value of `straighten()`
- Version 0.1.0 released

### Installation

```{r eval=FALSE}
devtools::install_github("hrbrmstr/curlconverter")
```

```{r echo=FALSE, message=FALSE, warning=FALSE, error=FALSE}
options(width=120)
```

### Usage

```{r}
library(curlconverter)
library(jsonlite)
library(httr)

# current verison
packageVersion("curlconverter")
```

Simple example using a call to <https://httpbin.org/headers>:

```{r}
httpbinrhcurl <- "curl 'https://httpbin.org/headers' -H 'pragma: no-cache' -H 'accept-encoding: gzip, deflate, sdch' -H 'accept-language: en-US,en;q=0.8' -H 'upgrade-insecure-requests: 1' -H 'user-agent: Mozilla/5.0 (Macintosh; Intel Mac OS X 10_11_3) AppleWebKit/537.36 (KHTML, like Gecko) Chrome/49.0.2623.39 Safari/537.36' -H 'accept: text/html,application/xhtml+xml,application/xml;q=0.9,image/webp,*/*;q=0.8' -H 'cache-control: no-cache' -H 'referer: https://httpbin.org/' --compressed"

straight <- straighten(httpbinrhcurl)
res <- make_req(straight)

# or 

straighten(httpbinrhcurl) %>% 
  make_req() -> res

toJSON(content(res[[1]](), as="parsed"), pretty=TRUE)
```

Slightly more complex one:

```{r}
toJSON(straighten("curl 'http://financials.morningstar.com/ajax/ReportProcess4HtmlAjax.html?&t=XNAS:MSFT&region=usa&culture=en-US&cur=&reportType=is&period=12&dataType=A&order=asc&columnYear=5&curYearPart=1st5year&rounding=3&view=raw&r=973302&callback=jsonp1454021128757&_=1454021129337' -H 'Cookie: JSESSIONID=5E43C98903E865D72AA3C2DCEF317848; sfhabit=asc%7Craw%7C3%7C12%7CA%7C5%7Cv0.14; ScrollY=0' -H 'DNT: 1' -H 'Accept-Encoding: gzip, deflate, sdch' -H 'Accept-Language: en-US,en;q=0.8' -H 'User-Agent: Mozilla/5.0 (Macintosh; Intel Mac OS X 10_11_3) AppleWebKit/537.36 (KHTML, like Gecko) Chrome/47.0.2526.111 Safari/537.36' -H 'Accept: text/javascript, application/javascript, */*' -H 'Referer: http://financials.morningstar.com/income-statement/is.html?t=MSFT&region=usa&culture=en-US' -H 'X-Requested-With: XMLHttpRequest' -H 'Connection: keep-alive' -H 'Cache-Control: max-age=0' --compressed"), pretty=TRUE)
```

There are some built-in test files you can play with:

```{r}
(curl_line <- readLines(system.file("extdata/curl5.txt", package="curlconverter"), warn=FALSE))

toJSON(straighten(curl_line, quiet=TRUE), pretty=TRUE)
(curl_line <- readLines(system.file("extdata/curl8.txt", package="curlconverter"), warn=FALSE))

# example with query parameters in the body
req <- straighten(curl_line, quiet=FALSE)

# ugh
(req[[1]]$data)

#yay!
toJSON(parse_query(req[[1]]$data), pretty=TRUE)
```

Spinning straw into gold

```{r}
curl_line <- c('curl "http://anasim.iet.unipi.it/moniqa/php/from_js.php" -H "Origin: http://anasim.iet.unipi.it" -H "Accept-Encoding: gzip, deflate" -H "Accept-Language: it-IT,it;q=0.8,en-US;q=0.6,en;q=0.4" -H "User-Agent: Mozilla/5.0 (Windows NT 6.3; WOW64) AppleWebKit/537.36 (KHTML, like Gecko) Chrome/48.0.2564.103 Safari/537.36" -H "Content-Type: application/x-www-form-urlencoded; charset=UTF-8" -H "Accept: */*" -H "Referer: http://anasim.iet.unipi.it/moniqa/" -H "X-Requested-With: XMLHttpRequest" -H "Connection: keep-alive" --data "deviceid=65&function_name=extract_measurements" --compressed')

straighten(curl_line) %>% 
  make_req() -> get_data

toJSON(content(get_data[[1]](), as="parsed"), pretty=TRUE)
```

That also sends this to the console and clipboard:

```{r eval=FALSE}
VERB(verb = "POST", 
     url = "http://anasim.iet.unipi.it/moniqa/php/from_js.php", 
     add_headers(Origin = "http://anasim.iet.unipi.it", 
                 `Accept-Encoding` = "gzip, deflate", 
                 `Accept-Language` = "it-IT,it;q=0.8,en-US;q=0.6,en;q=0.4", 
                 `User-Agent` = "Mozilla/5.0 (Windows NT 6.3; WOW64) AppleWebKit/537.36 (KHTML, like Gecko) Chrome/48.0.2564.103 Safari/537.36", 
                 Accept = "*/*", 
                 Referer = "http://anasim.iet.unipi.it/moniqa/", 
                 `X-Requested-With` = "XMLHttpRequest", 
                 Connection = "keep-alive"), 
     body = list(deviceid = "1", 
                 function_name = "extract_measurements"), 
     encode = "form")
```

### Test Results

```{r}
library(curlconverter)
library(testthat)

date()

test_dir("tests/")
```

### Code of Conduct

Please note that this project is released with a [Contributor Code of Conduct](CONDUCT.md). 

By participating in this project you agree to abide by its terms.
